---
title: "Assignment 1"
---

# Assignment 1

My first assignment has three parts.

## b) Differences between R and Python

### Indexing Elements

One of the main difference between these two popular languages is indexing the elements. R uses 1 as base index number, but in python indexing starts with 0.

For example:

```{r}
# In R
a <- c(4, 5, 6, 7)
first_a <- a[1]
second_a <- a[2]
print(first_a)
print(second_a)
```

```{python}
# In Python
b = [4, 5, 6, 7]
first_b = b[0]
second_b = b[1]
print(first_b)
print(second_b)
```

## Syntax Differences

One of the other difference is syntax. For example, to assign an element in R we use "\<-" but, in Python it is "=".

```{R}
a <- 1
b <- 2
summation <- a + b
print(summation)
```

```{python}
x = 2 
y = 3
summation = x + y
print(summation)
```

## Creating Data Frame

R has special data structures like factors and data frames, but in python data structures differs like lists, dictionaries and pandas data frames.

```{r}
Turkish_cities <- data.frame(
                            city_name = c("Izmir", "Istanbul", "Ankara"),
                            city_population = c("4.300.000", "16.000.000", "5.700.000")
                            )
```

```{python}
import pandas as pd 
turkish_cities= [["Izmır", 4.300.000], ["Istanbul", 16.000.000], ["Ankara", 5.700.000]]
df= pd.dataframe(turkish_cities,columns= ["city_name", city_population])

```
